Paper 1 Analysis

### 2015-11-11 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Beginning a table for Paper 1.

>>>>

<<Other_Models_Results>>=
  # PT, unadjusted kl, quality-adjusted e
  summary(other_models$PT$uakl_qae)
  naturalCoef(other_models$PT$uakl_qae)
  sum(resid(other_models$PT$uakl_qae)^2)

  # PT, quality-adjusted kl, unadjusted e
  summary(other_models$PT$qakl_uae)
  naturalCoef(other_models$PT$qakl_uae)
  sum(resid(other_models$PT$qakl_uae)^2)

  # UK, unadjusted kl, quality-adjusted e
  summary(other_models$UK$uakl_qae)
  naturalCoef(other_models$UK$uakl_qae)
  sum(resid(other_models$UK$uakl_qae)^2)

  # UK, quality-adjusted kl, unadjusted e
  summary(other_models$UK$qakl_uae)
  naturalCoef(other_models$UK$qakl_uae)
  sum(resid(other_models$UK$qakl_uae)^2)
@

This is a table for Paper 1.

<<Other_Models_table>>=
  # Start with the exponential-only (reference) models
  OMTable <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
    list(Model = "Ref.",
         Country=id[[1]],
         kl = NA,
         e = NA,
         Nest = NA,
         lambda = coef(modelsExp[[id[[1]]]])[[2]],
         lambda_ratio = 1,
         SSE = sum(resid(mod)^2))
  }) %>% bind_rows()

  # Add all CES models
  OMTable <- leaf_apply(models, class="cesModel", f=function(mod, id){
  id_components <- strsplit(id, split = "[.]")[[1]]
  list(Model = "CES",
       Country = id_components[[1]],
       kl = id_components[[2]],
       e = id_components[[2]],
       Nest = id_components[[5]],
       lambda = naturalCoef(mod)$lambda,
       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
       SSE = sum(resid(mod)^2))
  }) %>% bind_rows() %>% bind_rows(OMTable, .)

  # Add the off-axis models
  OMTable <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
    id_components <- strsplit(id, split = "[.]")[[1]]
    print(id_components)
    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
    print(adjusted_components)
    list(Model = "CES",
         Country = id_components[[1]],
         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
         Nest = "kle",
         lambda = naturalCoef(mod)$lambda,
         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
         SSE = sum(resid(mod)^2)
         )

  }) %>% bind_rows() %>% bind_rows(OMTable, .)

  OMTable <- 
    # Keep only rows that we want
    filter(OMTable, is.na(Nest) | Nest == "kl" | Nest == "kle")
